Online resolving assembly graph by ONT long reads data

### 2019-07-05 paper.tex
sf

Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variances of coverage values. 
For that reason, they are only used as augmented information to calculate candidate paths' score in the next step.

%\subsection*{Untangling assembly graph by stream of nanopore data.}
\subsection*{Building bridges in real-time}
Bridge is the data structure designed for tracking the possible connections between two unique contigs (anchor nodes in the assembly graph).
Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences are identified and assigned in appropriate unique paths.

@@

\subsection*{Result extraction and output}
\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result.
A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if every edge along the path, $e_i, \forall i=1,\ldots,k$, must be the only option to traverse from either $v_{i-1}$ or $v_i$ following the transition rule.
To decompose the graph, we can just simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}. These edges are defined as branching edges which stop straight paths from further extending.

\begin{figure}[!hpt]
\centering
\includegraphics[width=.6\textwidth]{images/decompose.pdf}
\caption[Example of graph decomposition into longest straight paths]{Example of graph decomposition into longest straight paths. Branching edges are masked out (shaded) leaving only straight paths (bold colored) to report. There would be 3 contigs extracted by traversing along the straight paths here.}
\label{figure:npgraph_decompose}
\end{figure}
The decomposed graph is only used to report the contigs that can be extracted from an assembly graph at certain time point. For that reason, the branching edges are only masked but not removed from the original graph as they would be used for further bridging.

>>>>

Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variation of coverage values. 
For that reason, in \npgraph{}'s algorithm, they are only used as augmented information to calculate likelihood scores of candidate paths containing corresponding nodes.

%\subsection*{Untangling assembly graph by stream of nanopore data.}
\subsection*{Building bridges in real-time}
Bridge is the data structure designed for tracking the possible connections between two unique contigs (anchor nodes in the assembly graph).
Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences have been already identified and assigned in appropriate unique paths.

@@

\subsection*{Result extraction and output}
\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note4}).
